---
title: "Titanic_Machine_learning"
author: "Srikar"
date: "11 March 2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## libraries
``` {r}
library(ggplot2)
library(dplyr)
```
## Load Dataset
Seperate the values by
Replace the string empty values with NA

```{r}
dataset <- read.csv(file = "train.csv",header = TRUE, sep = ",",na.strings=c("","NA"))

head(dataset)
```
## Find the Columns with null values
```{r}
sapply(dataset, function(x) sum((is.na(x))))

```
## Replace NA values with 
```{r}
```
## Check the impact of Sex on Survival rate
Males survived low when compared to females
```{r}
ggplot(dataset)+aes(x = Survived, fill = Sex)+geom_bar(width = 0.25,position = "dodge")
```


## Check the impact of Pclass on Survival rate
Pclass = 3 has less the least survival rate
```{r}
dataset$Pclass <- as.factor(dataset$Pclass)
ggplot(dataset)+aes(x = Survived, fill = Pclass)+geom_bar(width = 0.25,position = "dodge")
```

```{r}
mod_traininset <- dataset %>% select(-Cabin,-PassengerId,-Name, - Ticket)
head(mod_traininset)

```
## replace the Age = Null with appropriate values
```{r}
mod_traininset <- mod_traininset%>%
    mutate(Age = replace(Age,is.na(Age) & Pclass == 1, 37)) %>%
      mutate(Age = replace(Age,is.na(Age) & Pclass == 2, 29)) %>%
      mutate(Age = replace(Age,is.na(Age) & Pclass == 3, 24))
head(mod_traininset)

  
```
```{r}
library(caTools)
set.seed(123)
split = sample.split(mod_traininset$Survived, SplitRatio = 0.8)
training_set = subset(mod_traininset, split == TRUE)
test_set = subset(mod_traininset, split == FALSE)
# Fitting Logistic Regression to the Training set
classifier = glm(formula = Survived ~ .,
                 family = binomial,
                 data = training_set)

summary(classifier)


```
As the significance of Parch and Fare is low.
Eliminating the columns Parch and Fare
```{r}
mod_traininset <- select(mod_traininset, -Parch, -Fare)

set.seed(123)
split = sample.split(mod_traininset$Survived, SplitRatio = 0.8)
training_set = subset(mod_traininset, split == TRUE)
test_set = subset(mod_traininset, split == FALSE)
# Fitting Logistic Regression to the Training set
classifier = glm(formula = Survived ~ .,
                 family = binomial,
                 data = training_set)

summary(classifier)

```

```{r}
# Predicting the Test set results
prob_pred = predict(classifier, type = 'response', newdata = select(test_set, -Survived))
y_pred = ifelse(prob_pred > 0.5, 1, 0)


# Making the Confusion Matrix
cm = table(test_set$Survived, y_pred > 0.5)
cm
```

